Fusing Filters with Integer Linear Programming

### 2014-05-15 2014betterfusionforfilters/Main.tex
remove manuel as author; add to acknowledgements

\authorinfo{ 
  Amos Robinson$^\dagger$ 
  \and Ben Lippmeier$^\dagger$
  \and Manuel M. T. Chakravarty$^\dagger$
  \and Gabriele Keller$^\dagger$ 
}{
  \vspace{5pt}
  \shortstack{
    $^\dagger$Computer Science and Engineering \\
    University of New South Wales, Australia \\[2pt]
    \textsf{\{amosr,benl,chak,keller\}@cse.unsw.edu.au}
  }
}

@@

\section*{Acknowledgements}
Many thanks are due to
Robert Clifton-Everest,
Kai Engelhardt,
Bill Kroon,
Frederik Madsen,
Abdallah Saffidine,
Carter Schonwald,
and Jingling Xue
for enlightening discussions relating to this work.

>>>>

\authorinfo{ 
  Amos Robinson$^\dagger$ 
  \and Ben Lippmeier$^\dagger$
  \and Gabriele Keller$^\dagger$ 
}{
  \vspace{5pt}
  \shortstack{
    $^\dagger$Computer Science and Engineering \\
    University of New South Wales, Australia \\[2pt]
    \textsf{\{amosr,benl,keller\}@cse.unsw.edu.au}
  }
}

@@

\section*{Acknowledgements}
Many thanks are due to
Manuel Chakravarty,
Robert Clifton-Everest,
Kai Engelhardt,
Bill Kroon,
Frederik M.\ Madsen,
Abdallah Saffidine,
Carter Schonwald,
and Jingling Xue
for enlightening discussions relating to this work.
